The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-20 albatros_paper.tex
HCC added first draft of acknowledgments

We are extremely grateful for the anemic carrots on Marion.  Yum.

>>>>

We gratefully acknowledge the National Research Foundation (grant
number 110929) and the South African National Antarctic Programme for
providing funding and logistical support for our research program.
The financial assistance of the South African SKA Project (SKA SA)
towards this research is hereby acknowledged (\url{www.ska.ac.za}).
We additionally extend our sincere gratitude to the staff at SKA SA
for hosting our lab tests.  We thank the South African National Space
Agency for their technical support, the crew of Ultimate Heli for
safely delivering us and our cargo, and all of the Marion takeover and
winter team members who provided invaluable advice and field help.
The authors also wish to thank members of the LWA and RAPID
collaborations for useful discussions.
